---
title: "Practical Machine Learning"
author: "Eddie Warner"
output:
  html_document:
    keep_md: yes
    theme: united
  pdf_document: default 
  
references:
- URL: http://groupware.les.inf.puc-rio.br/har#weight_lifting_exercises
  author:
  - given: Wallace
  - family: Ugulino
  - given: Eduardo
  - family: Velloso
  - given: Hugo
  - family: Fuks
  id: Webstie_HAR
  title: Human Activity Recognition
---

## Synopsis

Human activity recognition - HAR - examines data gathered through monitors like *Jawbone Up*, *Nike FuelBand*, *Fitbit*, *Apple Watch*, *Basis Peak* etc. to quantify activity to address any number of applications.  Applications include, energy expenditure for weight-loss programs, monitoring of the elderly and monitoring fitness activity of a person or population to reach fitness goals. A novel question posed by the data set examined by this anlysis **Weight Lifting Exercises Dataset** is if training or qualitative measure like training can measured through the data. For a more complete description for the questions that initialed the study 

```{r loadlibraries, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

library(data.table)
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(reshape2)

require(grid)
require(gridExtra)

library(caret)

library(knitr)

opts_chunk$set(out.width='900px', dpi=200)
```

## Data Processing

```{r data, echo=TRUE, cache=TRUE}
    
file.name.train <- "pml-training.csv"
file.url.train <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

file.name.test <- "pml-testing.csv"
file.url.test <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

if(!file.exists(file.name.train)) {
    download.file(url = file.url.train, destfile = file.name.train)
}

if(!file.exists(file.name.test)) {
    download.file(url = file.url.test, destfile = file.name.test)
}

train_data <- as.data.table(read.csv(file.name.train, stringsAsFactors=FALSE, strip.white=TRUE))

test_data <- as.data.table(read.csv(file.name.test, stringsAsFactors=FALSE, strip.white=TRUE))

dim(train_data)
summary(train_data)
```

## Data Exploration

## Analysis

## References

## Appendix


